
% http://ryandlane.com/blog/2014/08/04/moving-away-from-puppet-saltstack-or-ansible/

% http://ryandlane.com/blog/2014/08/26/saltstack-masterless-bootstrapping/

\bibitem{NIST}
\newblock NIST, (2011). The NIST Definition of Cloud Computing [online] Available at: http://csrc.nist.gov/publications/nistpubs/800-145/SP800-145.pdf [Accessed 10 Oct. 2014].

\bibitem{OpenStack}
\newblock OpenStack.org, (2014). OpenStack Open Source Cloud Computing Software. [online] Available at: http://openstack.org [Accessed 12 Oct. 2014].

\bibitem{STACKALYTICS}
\newblock  Stackalytics.com, (2014). Stackalytics | OpenStack community contribution in Kilo release. [online] Available at: http://stackalytics.com [Accessed 12 Oct. 2014].

\bibitem{CERN}
\newblock  Information-technology.web.cern.ch, (2014). OpenStack Information. [online] Available at: http://information-technology.web.cern.ch/book/cern-private-cloud-user-guide/openstack-information [Accessed 12 Oct. 2014].

\bibitem{PayPal}
\newblock Openstack.org, (2014). PayPal : OpenStack Open Source Cloud Computing Software. [online] Available at: http://www.openstack.org/user-stories/paypal/ [Accessed 12 Oct. 2014].

\bibitem{fuel}
\newblock Wiki.openstack.org, (2014). Fuel - OpenStack. [online] Available at: https://wiki.openstack.org/wiki/Fuel [Accessed 13 Oct. 2014].

\bibitem{CloudServices}
\newblock Ivan Ivanov, Marten van Sinderen and Boris Shishkov, editors, (2012). Cloud Computing and Services Science. Springer Science, New York, USA.

% ontological standards

\bibitem{OntologyDefinition}
\newblock Ling Liu and M. Tamer Özsu, editors, (2009).Encyclopedia of Database Systems, Springer Science, New York, USA.

\bibitem{OWL}
\newblock W3C.org, (2004). Web Ontology Language (OWL). [online] Available at:  http://www.w3.org/2004/OWL [Accessed 12 Oct. 2014].

\bibitem{SOAOntology}
\newblock The Open Group, (2014). Service-Oriented Architecture Ontology, Version 2.0, Open Group, New York, USA.

\bibitem{OasisCM}
\newblock OASIS, (2013). Configuration Management Resource Definitions. [online] Available at: https://tools.oasis-open.org/version-control/browse/wsvn/oslc-ccm/trunk/specs/config-mgt.html [Accessed 8 Oct. 2014].

\bibitem{DCMITerms}
\newblock Dublin Core Metadata Initiative, (2012). DCMI Metadata Terms. [online] Available at: http://dublincore.org/documents/dcmi-terms/ [Accessed 11 Oct. 2014].

\bibitem{OBO}
\newblock Berkeley Bioinformatics Open Source Project, (2014). The Open Biological and Biomedical Ontologies. [online] Available at: http://www.obofoundry.org/ [Accessed 10 Oct. 2014].

\bibitem{ODA}
\newblock W3C.org, (2001). Ontology Driven Architectures and Potential Uses of the Semantic Web in Systems and Software Engineering. [online] Available at:
 http://www.w3.org/2001/sw/BestPractices/SE/ODA/ [Accessed 5 Oct. 2014].

\bibitem{OntologyComputing}
\newblock Youseff L., Butrico, M., Da Silva, D., (2008). Toward a Unified Ontology of Cloud Computing. Grid Computing Environments Workshop GCE '08, IEEE, USA.

\bibitem{OntologyEvolution}
\newblock Lucas de Oliveira Arantes, Ricardo de Almeida Falbo, Giancarlo Guizzardi, (2009). Evolving a Software Configuration Management Ontology, IEEE

%\bibitem{ReClass}
%\newblock {\em reclass. Recursive external node classification }
%\newblock http://reclass.pantsfullofunix.net/


% ontological applications

%\bibitem{Pellet}
%\newblock {\em Pellet: OWL 2 Reasoner for Java }
%\newblock http://clarkparsia.com/pellet/

% Cloud computing deployment tools and config management tools

%\bibitem{OpenStackFuel}
%\newblock {\em OpenStack. Fuel Wiki }
%\newblock https://wiki.openstack.org/wiki/Fuel

%\bibitem{DevStack}
%\newblock {\em Fedora Project. OpenStack devstack}
%\newblock http://fedoraproject.org/wiki/OpenStack\_devstack

%\bibitem{Cfengine}
%\newblock {\em CFEngine. FCEngine 3.5 Documentation }
%\newblock https://cfengine.com/docs/3.5/index.html

%\bibitem{Foreman}
%\newblock {\em The Foreman. The Manual: Compute Resources }
%\newblock http://theforeman.org/manuals/1.4/index.html

% Metadata storage and retreival systems

%\bibitem{PuppetHiera}
%\newblock {\em Puppet Labs. Creating Hierarchies }
%\newblock http://docs.puppetlabs.com/hiera/1/hierarchy.html

